An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-04 docs/icccn2009/paper.tex
Some text on DSP Components
git-svn-id: svn://localhost/netbeams/trunk@332 559edde2-a4d4-44e0-96fc-4035e40d7396

\subsection{Components}

>>>>

\subsection{DSP Components}

A DSP Component encapsulates a particular functionality. We
distinguish between those components that produce data (DP) and those
that consume data (DC). An example for a DSP Component acting in the
role of a DP is a sensor module. The sensor module reads data from the
physical sensor and converts the data into a message that is forwarded
to the DSP. Because this module generates data with respect to the
DSP, it is a data producer. An example for a data consumer is a
converter module that converts the internal, DSP-specific data format,
suitable for consumption by external applications. One such common
format used in the domain of environmental monitoring is OpenDAP
(REF). Since the converter module accepts messages from the DSP, it
acts in the role of a data consumer. Finally, a DSP Component
implementing persistency is an example of a module that acts in the
roles of both data producer and consumer. It accepts messages from the
DSP and stores them in a database. At a later time, it may act as a
data producer by resending previously stored messages.

In order to enrich the DSP, a programmer has to implement new DSP
Components.
